```latex
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}




\begin{document}


\begin{center}
    \textbf{\Huge \scshape Anmol Bhardwaj} \\ \vspace{1pt}
    \small  $|$\href{mailto:anmol03kw@gmail.com}{\underline{anmol03kw@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/anmol-bhardwaj-55374321a/}{\underline{linkedin.com/in/anmol-bhardwaj-55374321a/}} $|$
    \href{https://github.com/Anmol-2003}{\underline{github.com/Anmol-2003}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Delhi Technological University}{}
      {}{November 2022 -- August 2026}
      \resumeItemListStart
        \resumeItem{Grade: 8.46}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Data Engineer}{February 2024 -- April 2024}
      {RizzAI}{}
      \resumeItemListStart
        \resumeItem{Developed a scraping pipeline to fetch data from multiple online e-commerce platforms.}
        \resumeItem{Implemented an asynchronous script for CRUD operations in Postgres on a large scale.}
        \resumeItem{Automated the entire data acquisition pipeline.}
      \resumeItemListEnd

    \resumeSubheading
      {AI Research Intern}{December 2023 -- February 2024}
      {GoldSmiths University, London}{}
      \resumeItemListStart
        \resumeItem{Developed an ensemble for classification of MBTI personality traits with multimodal inputs using RoBERTa and Random Forest Regressor.}
        \resumeItem{Achieved 95.8\% accuracy, handling the high imbalance using SMOTE and other NLP augmentation strategies like lemmitization.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{RailMadadv2}}{}
          \resumeItemListStart
            \resumeItem{An end-to-end complaint management system for Indian Railways.}
            \resumeItem{Utilizes Python, MongoDB, and Parallel Programming, and features a chat-bot developed using an agentic framework with Gemini as core LLM and a 2-click form interface for registering complaint and reducing the registration time by 50\%.}
            \resumeItem{Supports multilingual and multimodal inputs.}
            \resumeItem{Complaint categorization and sub-categorization done with LLaMa-3.3-70B achieving 99.8\% accuracy.}
            \resumeItem{Employs SOTA multi-modal models for extracting description from multi-modal inputs.}
            \resumeItem{Smart reassignment of complaints amongst staffs (smart queues) of the same department to increase customer satisfaction and resolution rate.}
            \resumeItem{Implements polling and complaint aggregation based on contextual similarity to update complaint priority and reduce starvation.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{SocioTrackr}}{}
          \resumeItemListStart
            \resumeItem{Developed a web application that performs analysis on texts, images, and videos to provide an insight on viewer perception about social media profile.}
            \resumeItem{Works with Instagram, YouTube, and Reddit.}
            \resumeItem{Deployed SOTA LLM models on Google Cloud to perform sentiment analysis, emotion classification, and other video and image analysis using CLIP and BLIP architectures.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{KeyValueDB}}{}
          \resumeItemListStart
            \resumeItem{A key-value LSM tree database developed from scratch using C++.}
            \resumeItem{Employed skip list data structure for memTable and write ahead log for availability.}
            \resumeItem{Managed concurrency using mutex locks, between write, memTable save to disk, and compaction operations, thus providing consistency to database state.}
            \resumeItem{Used tombstone approach for persisting deletion of data in the database.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C++, Javascript(Basic), SQL} \\
     \textbf{Frameworks}{: FastAPI, Flask, Django, Express.js, React.js, Tensorflow, Pytorch, SQLAlchemy, huggingface} \\
     \textbf{Certifications}{: Machine Learning Specialization, MLOps specialization} \\
     \textbf{Courses}{: Data structures and Algorithms, object oriented programming, Operating systems, Computer Networks, Distributed Systems, Database management systems}
    }}
 \end{itemize}
\end{document}
```